Universal Anonymous Signatures

### 2022-07-03 prism-backend/research/gsac/app-building-blocks.tex
Updated UAS proofs. Missing proof for new property obt-anon.
Fixing flaws in definitions and non-frame proof. (non-frame not done.)

\begin{figure}[ht!]
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpComBind(\Csecpar)$}{%
      \Cparm \gets \CSetup(\Csecpar) \\
      (\msg_0,r_0,\msg_1,r_1) \gets \adv(\Cparm) \\
      \Ccom_0 \gets \CCommit(\Cparm,\msg_0,r_0) \\
      \Ccom_1 \gets \CCommit(\Cparm,\msg_1,r_1) \\
      \pcif \msg_0 \neq \msg_1 \land \Ccom_0 = \Ccom_1: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpComHideb(\secpar)$}{%
      \Cparm \gets \CSetup(\secpar) \\
      (\msg_0,\msg_1,st) \gets \adv(\Cparm) \\
      r \getr \mathcal{R} \\
      \Ccom \gets \CCommit(\Cparm,\msg_b,r) \\
      b' \gets \adv(st,\Ccom) \\
      \pcreturn b'
    }
  \end{minipage}
  \label{fig:com-games}
  \caption{Games for commitment schemes.}
\end{figure}

@@

Any zero-knowledge proof of knowledge must meet completeness, soundness and
zero-knowledge,properties. We further need an extra property, called
\emph{simulation-extractability} \cite{cl06}, which amplifies the security
requirements of simulation soundness.
%
To define more formally the properties we need, we have to define three extra
algorithms:

@@

When we want to make explicit the NP relation \NIZKRel to which the previous
algorithms refer to, we use $\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel$, 
$\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and subindex when clear
from context. Altogether, the tuple $(\Setup,\Prove,\Verify,\SimSetup,\Sim,
\Extract)$ needs to meet the following properties:

>>>>

\begin{figure}[ht!]
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpComBind(\Csecpar)$}{%
      \Cparm \gets \CSetup(\Csecpar) \\
      (\msg_0,r_0,\msg_1,r_1) \gets \adv(\Cparm) \\
      \Ccom_0 \gets \CCommit(\Cparm,\msg_0,r_0) \\
      \Ccom_1 \gets \CCommit(\Cparm,\msg_1,r_1) \\
      \pcif \msg_0 \neq \msg_1 \land \Ccom_0 = \Ccom_1: \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpComHideb(\secpar)$}{%
      \Cparm \gets \CSetup(\secpar) \\
      b' \gets \adv^{COM(\Cparm,\cdot,\cdot)},~\textrm{where}: \\
      \pcind COM(\Cparm,\msg_0,\msg_1): \\
      \pcind \pcind r \getr \mathcal{R};~\pcreturn \CCommit(\Cparm,\msg_b,r) \\
      % (\msg_0,\msg_1,st) \gets \adv(\Cparm) \\
      % r \getr \mathcal{R} \\
      % \Ccom \gets \CCommit(\Cparm,\msg_b,r) \\
%      b' \gets \adv(st,\Ccom) \\
      \pcreturn b'
    }
  \end{minipage}
  \label{fig:com-games}
  \caption{Games for commitment schemes.}
\end{figure}

@@

Any zero-knowledge proof of knowledge must meet completeness, soundness and
zero-knowledge,properties. We further need an extra property, called
\emph{simulation-extractability} \cite{cl06}, which amplifies the security
requirements of (simulation-) soundness.
%
To define more formally the properties we need, we have to define three extra
algorithms:

@@

When we want to make explicit the NP relation \NIZKRel to which the previous
algorithms refer to, we use $\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel$, 
$\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and superindex when
clear from context. Altogether, the tuple $(\Setup,\Prove,\Verify,\SimSetup,
\Sim,\Extract)$ needs to meet the following properties:

### 2022-07-03 prism-backend/research/gsac/formal-uas.tex
Undoing wrong change in model.
Fixing flaws in definitions and non-frame proof. (non-frame not done.)

        \procedure{$\CHALb(\oid,\cscid_{0,1},\msg,\feval)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \pcfor d \in \bin~ \exists \cid,\cid' \in \scid_d~\suchthat \\
          \pcind \cid \in \CRED \land \cid' \in \CCRED: \pcreturn \bot \\
          \pcif \oid \in \CO: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\          
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\CRED[\cscid_0],
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
          \pcif \Yeval \notin \rngfeval \lor \TYeval \notin \rngfeval:
          \pcreturn \bot \\
          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

\paragraph{Helper functions \ExtractIssue, \ExtractSign, \IdentifyCred, and
  \IdentifyUK.} We assume the existence of these four functions. They are not
functions available in the actual scheme, but rather to the challenger in the
experiments we use to formalize security of \UAS schemes. Similar techniques
have been used before to prove security in privacy-preserving schemes with some
sort of accountability, but that do not offer conventional opening as vanilla
group signatures. For instance, see related works on DAA \cite{bfg+11,cdl16} and
group signature variants \cite{dl21,fgl21,gl19,lnpy21}. More concretely, these
functions are as follows:

\begin{description}
\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
  credentials (if any) and their attributes involved in the request. It 
  needs an honest issuer as, otherwise, the transcripts won't be available.
\item[$\ExtractSign(\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
  \scred,\attrs_{\scred},\yeval^1,\yinsp)$.] Receives a signature \Sig,
  as well as the opener identifier \oid, and the identifiers of all issuers of
  the credentials used to produce the signature over \msg, and for \feval.
  It outputs the user secret key and credentials (with their attributes) used to
  generate the signature, and the $\yeval^1$ and \yinsp values.
\item[$\IdentifyCred(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
  Otherwise, it returns $0$. In order to be meaningful, this requires that,
  for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
  \IdentifyCred return $1$.
\item[$\IdentifyUK(\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret key.
  This is trivial for honest users, for which there must be a one-to-one
  relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
  to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
  to \uid, extract the used secret key, and check if there is a match. In the
  latter case, there is no guarantee of getting a one-to-one relationship
  between \usk and \uid. Also, when used for corrupt users, this can only be
  used when the issuer is honest, as transcripts are needed. 
\end{description}

@@

\begin{figure*}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpIssAnonb(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\OIssAnon} (\parm) \\
        \pcreturn b^*
      }
    \end{minipage}

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpSigAnonb(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\OSigAnon} (\parm) \\
        \pcreturn b^*
      }
    \end{minipage}
  }
  \caption{Issuance and signature anonymity experiments for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure*}

@@

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      \cid \gets \adv^{\Oforgeissue}(\parm) \\
      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trans[\cid]) \\
      \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
      \exists \cred \in \scred~\suchthat~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
  \label{fig:exp-uas-unfor-issue}
\end{figure}

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0: \pcreturn 1 \\
      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets \ExtractSign(\oid,\siid,\Sig,
      \msg,\feval) \\
      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1
      \lor \Yeval \notin \rngfeval:
      \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp'
      \lor \yinsp \neq \yinsp':
      \pcreturn 1 \\
      \pcif \exists \cred \in \scred~\suchthat~
      \IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
      \pcreturn 1 \\
      \pcif \nexists \uid~\suchthat~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
  \label{fig:exp-uas-unfor-sign}
\end{figure}

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
    \adv^{\Oframe}(\parm) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
    \pcreturn 0 \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
    \pcreturn 0 \\
    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
    \ExtractSign(\oid,\siid,\Sig,\msg,\feval) \\
    \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1
    \lor \Yeval \notin \rngfeval: \pcreturn 1 \\
    \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
    \lor \yinsp \neq \yinsp': \pcreturn 1 \\    
    \pcif \nexists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \pcreturn 0 \\
    \pcif \nexists (\cdot,\cdot,\Sig,\Yeval,\msg,\feval)
    \in \SIG[\uid]: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}

>>>>

        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \pcfor d \in \bin~ \exists \cid,\cid' \in \scid_d~\suchthat \\
          \pcind \cid \in \CRED \land \cid' \in \CCRED: \pcreturn \bot \\
          \pcif \oid \in \CO: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\          
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\CRED[\cscid_0],
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
          \pcif \Yeval \notin \rngfeval \lor \TYeval \notin \rngfeval:
          \pcreturn \bot \\
          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

\paragraph{Helper functions \SimSetup, \ExtractIssue, \ExtractSign,
  \IdentifyCred, and \IdentifyUK.} We assume the existence of these helper
functions. They are not functions available in the actual scheme, but rather to
the challenger in the experiments we use to formalize security of \UAS schemes.
Consequently, while we introduce them here and specify some conditions they need
to meet, their full definition is dependent on the construction. We fully define
them for our generic construction \CUASGen in \appref{app:uas-proofs}. Similar
techniques have been used before to prove security in privacy-preserving schemes
with some sort of accountability, but that do not offer conventional opening as
vanilla group signatures. For instance, see related works on DAA
\cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}.
More concretely, these functions are as follows:

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global (simulated) parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
  Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
  and returns the credentials (if any) and their attributes involved in the
  request. It needs an honest issuer as, otherwise, the transcripts won't be
  available. 
\item[$\ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
  \scred,\attrs_{\scred},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a
  signature \Sig,
  as well as the opener identifier \oid, and the identifiers of all issuers of
  the credentials used to produce the signature over \msg, and for \feval.
  It outputs the user secret key and credentials (with their attributes) used to
  generate the signature, and the $\yeval^1$ and \yinsp values.
\item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
  Otherwise, it returns $0$. In order to be meaningful, this requires that,
  for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
  \IdentifyCred return $1$.
\item[$\IdentifyUK(\trap,\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret
  key. This is trivial for honest users, for which there must be a one-to-one
  relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
  to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
  to \uid, extract the used secret key, and check if there is a match. In the
  latter case, there is no guarantee of getting a one-to-one relationship
  between \usk and \uid. Also, when used for corrupt users, this can only be
  used when the issuer is honest, as transcripts are needed. 
\end{description}

@@

\begin{figure*}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpIssAnonb(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        b^* \gets \adv^{\OIssAnon} (\parm) \\
        \pcreturn b^*
      }
    \end{minipage}

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpSigAnonb(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        b^* \gets \adv^{\OSigAnon} (\parm) \\
        \pcreturn b^*
      }
    \end{minipage}
  }
  \caption{Issuance and signature anonymity experiments for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure*}

@@

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
      \cid \gets \adv^{\Oforgeissue}(\parm) \\
      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
      \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
      \exists \cred \in \scred~\suchthat~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
  \label{fig:exp-uas-unfor-issue}
\end{figure}

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
      (\parm,\trap) \gets \Setup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0: \pcreturn 1 \\
      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets
      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1
      \lor \Yeval \notin \rngfeval:
      \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp'
      \lor \yinsp \neq \yinsp':
      \pcreturn 1 \\
      \pcif \exists \cred \in \scred~\suchthat~
      \IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
      \pcreturn 1 \\
      \pcif \nexists \uid~\suchthat~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
  \label{fig:exp-uas-unfor-sign}
\end{figure}

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
    (\parm,\trap) \gets \SimSetup(1^\secpar) \\
    (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
    \adv^{\Oframe}(\parm) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
    \pcreturn 0 \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
    \pcreturn 0 \\
    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
    \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
    \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1
    \lor \Yeval \notin \rngfeval: \pcreturn 1 \\
    \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
    \lor \yinsp \neq \yinsp': \pcreturn 1 \\    
    \pcif \nexists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \pcreturn 0 \\
    \pcif \nexists (\cdot,\cdot,\Sig,\Yeval,\msg,\feval)
    \in \SIG[\uid]: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}
